---
title: ""
author: ""
date: ""
output: 
  word_document
  
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages= FALSE, warning= FALSE, comment = NA, fig.width = 7, fig.height=7)
knitr::opts_knit$set(root.dir=normalizePath('../'),fig.align="center")
#devtools::install_github("haozhu233/kableExtra")

options(scipen=999, digits=2)

library("lubridate")
library("ggplot2")
library("dplyr")
library("viridis")
library("tidyverse")
library("scales")
library("waterData")
library("gridExtra")
library("cowplot")
library('ggpubr')
library("reshape2")

#sourcing the function
source("oyster_functions.R")
```


```{r organize, include= FALSE}
data <- read.csv("data//transect_data.csv", header= TRUE)
org_data <- organizeData(data)
cal_den<- calculateCountsDensity(data,org_data)

### days sampled for all time
total_days <- length(unique(org_data$date))

total_days_22 <- length(unique(org_data$date[org_data$date > "2020-08-01"]))
```



```{r 2022_local, echo=FALSE,comment=NA}

# Colors for periods
#18- CC79A7 (pink)
#20-E69F00 (orange)
#22-56B4E9 (blue)


current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))
current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes(y= density, fill=as.factor(period))) +
  geom_boxplot()+
  ylim(0,500) +
  ylab("Oyster density per m^2")+
  labs(title= "Live Oyster Density by Locality for Periods 18, 20, and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))+
  facet_wrap(~locality)

```
Figure- Calculated live oyster density by locality for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r,echo=FALSE,comment=NA}

current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes( y= density_dead, fill=as.factor(period))) +
  geom_boxplot() +
  ylim(0,150) +
  ylab("Oyster density per m^2")+
  labs(title= "Dead Oyster Density by Locality for Periods 18, 20, and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
  facet_wrap(~locality)
```
Figure- Calculated dead oyster density by locality for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r 2022_strata,echo=FALSE,comment=NA }

current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))
current_plot$strata <- factor(current_plot$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes(y= density, fill=as.factor(period))) +
  geom_boxplot() +
  ylim(0,500) +
  ylab("Oyster density per m^2")+
  labs(title= "Live Oyster Density by Strata for Periods 18, 20 and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2)

```
Figure- Calculated live oyster density by strata for  periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage


```{r,echo=FALSE,comment=NA}
current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22"))
current_plot$strata <- factor(current_plot$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22) %>% 
  ggplot( aes(y= density_dead, fill=as.factor(period))) +
  geom_boxplot()+ 
  ylim(0,150) +
  ylab("Oyster density per m^2")+
  labs(title= "Dead Oyster Density by Strata for Periods 18, 20 and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2)
```
Figure- Calculated dead oyster density by strata for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020) and 22 (Winter 2020-2021) with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage
