---
title: "Transect Report Lone Cabbage"
author: ''
date: ''
output:
  pdf_document: default
  html_document:
    df_print: paged
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, messages= FALSE, warning= FALSE, comment = NA, fig.width = 7, fig.height=7)
knitr::opts_knit$set(root.dir=normalizePath('../'),fig.align="center")
#devtools::install_github("haozhu233/kableExtra")

options(scipen=999, digits=2)

library("lubridate")
library("ggplot2")
library("dplyr")
library("viridis")
library("tidyverse")
library("scales")
library("waterData")
library("gridExtra")
library("cowplot")
library('ggpubr')
library("reshape2")
library("tinytex" )

#sourcing the function
source("oyster_functions.R")
```

```{r organize, include= FALSE}
data <- read.csv("data//transect_data.csv", header= TRUE)
org_data <- organizeData(data)
cal_den<- calculateCountsDensity(data,org_data)

### days sampled for all time
total_days <- length(unique(org_data$date))

total_days_24 <- length(unique(org_data$date[org_data$date > "2021-08-01"]))
```

# Overview
This report provides summary statistics and figures for ongoing transect sampling. The first section of the report focuses on the current sampling (Winter 2021-2022) and how the collected data compare to last year's sampling (Winter 2020-2021). So far `r total_days_24` days have been sampled this season. The second half of the report gives summaries of all of the data that have been collected since the beginning of the project (`r head(org_data$date, 1)`). In total, `r total_days` days have been sampled over this entire project. 

## Definition of Localities
\begingroup\Large
| LOCALITY | LOCATION        |  
|:---------|----------------:|
| BT       | Big Trout       |   
| CK       | Cedar Key       |  
| CR       | Corrigan's Reef | 
| HB       | Horseshoe Beach | 
| LC       | Lone Cabbage    | 
| LT       | Little Trout    |  
| NN       | No Name         | 
\endgroup


## Definition of Strata
\begingroup\Large
| STRATA  | DEFINITION              |  
|:--------|------------------------:|
| Y_N    | Yes Harvest, No Rock     |   
| Y_Y    | Yes Harvest, Yes Rock    |  
| N_N    | No Harvest, No Rock      | 
| N_Y    | No Harvest, Yes Rock     | 
| N_PILOT| No Harvest, Pilot Rocks  |  
\endgroup


\newpage

# Current Sampling
Here, we provide a progress bar showing how much of the sampling has been completed for this season, plus summary tables and plots comparing live counts and density of oysters between this current season and last year. **The current sampling period is period 24, and last year's sampling period is period 22.** 

```{r progress_bar, echo=FALSE,comment=NA, fig.width = 7, fig.height = 6}
progress(org_data)
```

\newpage

## Summary Tables for Periods 18, 20, 22, and 24
These summary tables provide summary statistics on live counts and oyster densities for just periods **18 (Winter 2018-2019), 20 (Winter 2019-2020), 22 (Winter 2020-2021), and 24 (Winter 2021-2022).**   

Summary statistics include:    
- Locality  or Strata or Period 
- Mean  
- Median  
- Standard Deviation (SD)  
- Variance (Var)  
- Coefficient of variation (CV)  
- Standard Error (SE)  
- Lower 95% Confidence Interval assuming normal distribution (L95)  
- Upper 95% Confidence Interval assuming normal distribution (U95)  
- Bootstrap Mean (Bstrap Mean)  
- Lower 95% Confidence Interval from Bootstrap Values (L95 Bstrap)  
- Upper 95% Confidence Interval from Bootstrap Values (U95 Bstrap) 

### Summary of Live Counts for Periods 18, 20, 22, and 24
```{r 1824_tables, echo = FALSE, comment = NA}
p1824 <- subset(cal_den, cal_den$period == 18 | cal_den$period == 20 | cal_den$period == 22 | cal_den$period == 24)
options(width = 100) #used to make the page size "larger" in rmd to fit all the data from the tables

summaryCounts(p1824)
summaryDensity(p1824)
```
\newpage

### Summary of Dead Counts for Periods 18, 20, 22, and 24
```{r dead1824_tables, echo = FALSE, comment = NA}
p1824 <- subset(cal_den, cal_den$period == 18 | cal_den$period == 20 | cal_den$period == 22 | cal_den$period == 24)

options(width = 100) #used to make the page size "larger" in rmd to fit all the data from the tables

summarydeadCounts(p1824)
summarydeadDensity(p1824)
```
\newpage
## Summary Plots for Periods 18, 20, 22, and 24
  
```{r 1824_local, echo=FALSE,comment=NA}

# Colors for periods
#18- CC79A7 (pink)
#20- E69F00 (orange)
#22- 56B4E9 (blue)
#24- F0E442 (yellow)


current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22", "24"))
current_plot %>% 
  filter(period== 18 | period== 20 | period==22 | period==24) %>% 
  ggplot( aes(y= density, fill=as.factor(period))) +
  geom_boxplot()+
  ylab("Oyster density per m^2")+
  labs(title= "Live Oyster Density by Locality for Periods 18, 20, and 22", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9", "#F0E442"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))+
  facet_wrap(~locality)

```
Figure- Calculated live oyster density by locality for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020), 22 (Winter 2020-2021), and 24 (Winter 2021-2022) with the last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage

```{r,echo=FALSE,comment=NA}

current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22", "24"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22 | period==24) %>% 
  ggplot( aes( y= density_dead, fill=as.factor(period))) +
  geom_boxplot() +
  ylab("Oyster density per m^2")+
  labs(title= "Dead Oyster Density by Locality for Periods 18, 20, 22, and 24", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9", "#F0E442"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
  facet_wrap(~locality)
```
Figure- Calculated dead oyster density by locality for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020), 22 (Winter 2020-2021), and 24 (Winter 2021-2022) with the last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage

```{r 2022_strata,echo=FALSE,comment=NA }

current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22", "24"))
current_plot$strata <- factor(current_plot$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22 | period==24) %>% 
  ggplot( aes(y= density, fill=as.factor(period))) +
  geom_boxplot() +
  ylab("Oyster density per m^2")+
  labs(title= "Live Oyster Density by Strata for Periods 18, 20, 22, and 24", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9", "#F0E442"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2)

```
Figure- Calculated live oyster density by strata for  periods 18 (Winter 2018-2019), 20 (Winter 2019-2020), 22 (Winter 2020-2021), and 24 (Winter 2021-2022) with the last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage


```{r,echo=FALSE,comment=NA}
current_plot<- cal_den

current_plot$period <- factor(current_plot$period, levels = c("18", "20", "22", "24"))
current_plot$strata <- factor(current_plot$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

current_plot %>% 
  filter(period== 18 | period== 20 | period==22 | period==24) %>% 
  ggplot( aes(y= density_dead, fill=as.factor(period))) +
  geom_boxplot()+ 
  ylab("Oyster density per m^2")+
  labs(title= "Dead Oyster Density by Strata for Periods 18, 20, 22, and 24", fill= "Period") +
  scale_fill_manual(values=c("#CC79A7", "#E69F00", "#56B4E9", "#F0E442"))+
  theme(legend.position="right",panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2)
```
Figure- Calculated dead oyster density by strata for periods 18 (Winter 2018-2019), 20 (Winter 2019-2020), 22 (Winter 2020-2021), and 24 (Winter 2021-2022) with the last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage


The following summary plot is calculated in R using the `geom_density` (https://ggplot2.tidyverse.org/reference/geom_density.html) statistical function in `ggplot`. The `geom_density` function computes and draws kernel density estimates, which is then represented as a smoothed version of a histogram. 

    
```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 18 | period==20) %>% 
ggplot(aes(x=density, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Live Oyster Density by Period (18 and 20)", fill = "Period")+
          scale_fill_manual(values=c("#CC79A7", "#E69F00"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))

```
Figure- Calculated live oyster density by periods 18 (Winter 2018-2019) and 20 (Winter 2019-2020) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 18 | period==20) %>% 
ggplot(aes(x=density_dead, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Dead Oyster Density by Period (18 and 20)", fill = "Period")+
         scale_fill_manual(values=c("#CC79A7", "#E69F00"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))
```
Figure- Calculated dead oyster density by periods 18 (Winter 2018-2019) and 20 (Winter 2019-2020) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r den_plot, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 20 | period==22) %>% 
ggplot(aes(x=density, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Live Oyster Density by Period (20 and 22)", fill = "Period")+
          scale_fill_manual(values=c("#E69F00", "#56B4E9"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))

```
Figure- Calculated live oyster density by periods 20 (Winter 2019-2020) and 22 (Winter 2020-2021) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 20 | period==22) %>% 
ggplot(aes(x=density_dead, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Dead Oyster Density by Period (20 and 22)", fill = "Period")+
          scale_fill_manual(values=c("#E69F00", "#56B4E9"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))
```
Figure- Calculated dead oyster density by periods 20 (Winter 2019-2020) and 22 (Winter 2020-2021) using a probability density function with the last sample date of period 22 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 22 | period==24) %>% 
ggplot(aes(x=density, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Live Oyster Density by Period (22 and 24)", fill = "Period")+
          scale_fill_manual(values=c("#56B4E9", "#F0E442"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))

```
Figure- Calculated live oyster density by periods 22 (Winter 2020-2021) and 24 (Winter 2021-2022) using a probability density function with the last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

cal_den %>% 
  filter(period== 22 | period==24) %>% 
ggplot(aes(x=density_dead, fill = as.factor(period))) +
          geom_density(size = 1.5, alpha = 0.5)+
          xlab("Oyster density per m^2")+
          ylab("Probability Density Function")+
          labs(title = "Dead Oyster Density by Period (22 and 24)", fill = "Period")+
          scale_fill_manual(values=c("#56B4E9", "#F0E442"))+
          theme(panel.grid = element_blank(), panel.background = element_blank(), panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))
```
Figure- Calculated dead oyster density by periods 22 (Winter 2020-2021) and 24 (Winter 2021-2022) using a probability density function with the last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage

```{r, echo=FALSE, comment=NA, error= FALSE}

data1<- cal_den

data1$period <- factor(data1$period, levels = c("18", "20", "22", "24"))
data1$strata <- factor(data1$strata, levels = c("Y_Y", "Y_N", "N_Y", "N_N", "N_PILOT"))

  
  data1 %>% 
    filter(period== 18 | period== 20 | period==22 | period==24) %>% 
  ggplot(aes( x= count_live, y= count_dead, color= as.factor(period))) +
    geom_point(size=4) + 
    ylab("Dead Oyster Counts") +
    xlab("Live Oyster Counts") +
    labs(title= "Live and Dead Oyster Count Comparison for Periods 18, 20, 22, and 24", color= "Period") +
     scale_color_manual(values=c("#CC79A7", "#E69F00", "#56B4E9", "#F0E442"))+
    theme(legend.position="right",panel.grid = element_blank(), 
          panel.background = element_blank(), 
          panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"))+
    facet_wrap(~strata, ncol= 2)
```
Figure- Live and dead oyster count comparison by periods 18 (Winter 2018- 2019), 20 (Winter 2019-2020), 22 (Winter 2020-2021) and 24 (Winter 2021-2022), last sample date of period 24 as `r tail(org_data$date, 1)`.
\newpage

## Live Counts Double Pass Results
```{r, echo=FALSE, comment=NA, error= FALSE, fig.width = 6, fig.height = 6}


d2 <- org_data
  
  #subset for period 18+
  d3 <- subset(d2, d2$period > 17)
  

#need data in site x pass format
#rows are sites
#columns are passes
library(reshape2)
dp <- dcast(d3, date + period + locality + site + bar + station + transect + strata + tran_length ~ pass, value.var = "count_live")

#remove rows that don't have 2 passes
dp2 <- dp[is.na(dp$`2`) == FALSE,]

#compare pass 1 and pass 2 by period
dp2$diff <- dp2$`1`- dp2$`2`

#create a boxplot showing differences between pass 1 and pass 2 for periods 18,20,22, 24
boxplot(dp2$diff ~ dp2$period, xlab = "Period", ylab = "Difference in Live Counts b/w Passes")

```
  
Figure- Boxplot of the difference in live counts between pass 1 and pass 2 (pass 1 live counts - pass 2 live counts) for period 18, 20, 22, and 24

```{r, echo=FALSE, comment=NA, error= FALSE}
d2 <- org_data
  
  #subset for period 18+
  d3 <- subset(d2, d2$period > 17)
  

#need data in site x pass format
#rows are sites
#columns are passes
library(reshape2)
dp <- dcast(d3, date + period + locality + site + bar + station + transect + strata + tran_length ~ pass, value.var = "count_live")

#remove rows that don't have 2 passes
dp2 <- dp[is.na(dp$`2`) == FALSE,]

#compare pass 1 and pass 2 by period
dp2$diff <- dp2$`1`- dp2$`2`

#compare CV by locality (or strata) with period in different symbols

meanpass <- aggregate(diff ~ locality + period, data = dp2, FUN = "mean")
sdpass <- aggregate(diff ~ locality + period, data = dp2, FUN = "sd")

CV <- data.frame(locality = meanpass$locality, period = meanpass$period, mean_difference = meanpass$diff, sd_difference = sdpass$diff, CV = sdpass$diff/meanpass$diff)

print(CV, row.names = FALSE)
```
  
Table- Coefficient variation between pass 1 and pass 2, aggregated by locality and period for live counts  
\newpage

## Dead Counts Double Pass Results
```{r, echo=FALSE, comment=NA, error= FALSE, fig.width = 6, fig.height = 6}

d2 <- org_data
  
#subset for period 18+
d3 <- subset(d2, d2$period > 17)
dp <- dcast(d3, date + period + locality + site + bar + station + transect + strata + tran_length ~ pass, value.var = "count_dead")

#remove rows that don't have 2 passes
dp2 <- dp[is.na(dp$`2`) == FALSE,]

#compare pass 1 and pass 2 by period
dp2$diff <- dp2$`1`- dp2$`2`

#create a boxplot showing differences between pass 1 and pass 2 for periods 18,20,22,24
boxplot(dp2$diff ~ dp2$period, xlab = "Period", ylab = "Difference in Dead Counts b/w Passes")
```
  
Figure- Boxplot of the difference in dead counts between pass 1 and pass 2 (pass 1 dead counts - pass 2 dead counts) for period 18, 20, 22, and 24

```{r, echo=FALSE, comment=NA, error= FALSE}
d2 <- org_data
  
  #subset for period 18+
  d3 <- subset(d2, d2$period > 17)
  

#need data in site x pass format
#rows are sites
#columns are passes
library(reshape2)
dp <- dcast(d3, date + period + locality + site + bar + station + transect + strata + tran_length ~ pass, value.var = "count_dead")

#remove rows that don't have 2 passes
dp2 <- dp[is.na(dp$`2`) == FALSE,]

#compare pass 1 and pass 2 by period
dp2$diff <- dp2$`1`- dp2$`2`

#compare CV by locality (or strata) with period in different symbols

meanpass1 <- aggregate(`1` ~ locality + period, data = dp2, FUN = "mean")
meanpass2 <- aggregate(`2` ~ locality + period, data = dp2, FUN = 'mean')
sdpass1 <- aggregate(`1` ~ locality + period, data = dp2, FUN = "sd")
sdpass2 <- aggregate(`2` ~ locality + period, data = dp2, FUN = 'sd')

CV <- data.frame(locality = meanpass1$locality, period = meanpass1$period, CV_1 = sdpass1$`1`/meanpass1$`1`, CV_2 = sdpass2$`2`/meanpass2$`2`)

print(CV, row.names = FALSE)
```
  
Table- Coefficient variation between pass 1 and pass 2, aggregated by locality and period for dead counts


# Sampling for all Periods
Next, we provide summary tables and plots for all transect sampling. These data were collected between `r head(org_data$date, 1)` and `r tail(org_data$date, 1)`. The following are only for live oysters.

## Definitions of Periods
  

\begingroup\Large
  
    
| PERIOD  | SEASON  | YEAR       |
|:--------|:-------:|-----------:|
| 1       | Summer  | 2010       |  
| 2       | Winter  | 2010-2011  |  
| 3       | Summer  | 2011       | 
| 4       | Winter  | 2011-2012  |  
| 5       | Summer  | 2012       |
| 6       | Winter  | 2012-2013  | 
| 7       | Summer  | 2013       |
| 8       | Winter  | 2013-2014  |  
| 9       | Summer  | 2014       |  
| 10      | Winter  | 2014-2015  |  
| 11      | Summer  | 2015       |
| 12      | Winter  | 2015-2016  | 
| 13      | Summer  | 2016       | 
| 14      | Winter  | 2016-2017  |  
| 15      | Summer  | 2017       |
| 16      | Winter  | 2017-2018  | 
| 17      | Summer  | 2018       |
| 18      | Winter  | 2018-2019  |  
| 19      | Summer  | 2019       |
| 20      | Winter  | 2019-2020  | 
| 21      | Summer  | 2020       |
| 22      | Winter  | 2020-2021  |
| 23      | Summer  | 2021       |
| 24      | Winter  | 2021-2022  |
\endgroup

\newpage

## Summary of Effort for all Periods
These effort summaries show the total number of transects and total number of meters walked per locality, strata, locality per period, and strata per period. **These tables contain all data collected on the transects.**  

```{r effort, echo=FALSE, comment=NA, size= 10}
summaryEffort(cal_den)
```
\newpage
## Effort Plot Summaries for all Periods
```{r effort_plot,echo=FALSE, comment=NA}
effortPlot(cal_den)
```
\newpage

# Summary Tables for all Periods 
These summaries display summary statistics of live oysters by locality, strata, and period. These contain all data collected on the oyster transects.  
  
The summary statistics include:  
- Locality or Strata or Period
- Mean  
- Median  
- Standard Deviation (SD)  
- Variance (Var)  
- Coefficient of variation (CV)  
- Standard Error (SE)  
- Lower 95% Confidence Interval assuming normal distribution (L95)  
- Upper 95% Confidence Interval assuming normal distribution (U95)  
- Bootstrap Mean (Bstrap Mean)  
- Lower 95% Confidence Interval from Bootstrap Values (L95 Bstrap)  
- Upper 95% Confidence Interval from Bootstrap Values (U95 Bstrap)  
  

## Live Count Statistics for all Periods
```{r counts, echo=FALSE, comment=NA}
options(width = 100)
summaryCounts(cal_den)
```


## Live Density Statistics for all Periods
```{r density_tables, echo=FALSE, comment=NA}
options(width = 100)
summaryDensity(cal_den)
```
\newpage

## Dead Count Statistics for all Periods
```{r deadcounts, echo=FALSE, comment=NA}
options(width = 100)
summarydeadCounts(cal_den)
```
\newpage

## Dead Density Statistics for all Periods
```{r density_deadtables, echo=FALSE, comment=NA}
options(width = 100)
summarydeadDensity(cal_den)
```


## Summary Density Plots for all Periods
```{r plots, echo=FALSE, fig.height = 10}
plotsDensity(cal_den)
```
\newpage

```{r, echo=FALSE, fig.height = 8, fig.height = 8}
require(viridis)

data1<- cal_den

data1$strata <- factor(data1$strata, levels = c("Y_Y", "Y_N", "N_Y","N_N","N_PILOT"))

ggplot( data= data1, aes( x= count_live, y= count_dead)) +
  geom_point(size=4) + 
  ylab("Dead Oyster Counts") +
  xlab("Live Oyster Counts") +
  labs(title= "Live and Dead Count Comparison For All Periods", color= "Period") +
  #scale_color_viridis(option="heat",discrete=TRUE) +
  theme(legend.position="right",panel.grid = element_blank(), 
        panel.background = element_blank(), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid")) +
    facet_wrap(~strata, ncol= 2 )
```
Figure- Live and dead oyster comparison for all periods, last sample date of period 24 is `r tail(org_data$date, 1)`.
\newpage

# Summary Plots for Pilot Study Sites
A subset of the oyster transect locations were sampled over time for a pilot study. Here we provide plots of live oyster counts and density for these pilot stations with Lone Cabbage (LCO10B, LCO11A, LCO8B, LCO9A).  

```{r pilot_sites, echo=FALSE,comment=NA}
pilotSites(cal_den)
```
\newpage

# Latest Data Entered 
Displayed are the entries for the last date of sampling (`r tail(org_data$date, 1)`).   
```{r latest_data, echo=FALSE, comment=NA }
latest_obs<- org_data  %>% 
  filter(date == max(date)) %>% 
  select(date, station,tran_length,count_live, count_dead, treatment, strata)
print(latest_obs, row.names = FALSE)
     
```

